---
title: "analysis_units"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{analysis_units}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  out.width = "100%",
  dpi = 300,
  fig.width = 7.2916667,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(Rsequoia2)
library(sf)
library(tmap)
tmap_options(scale = 0.75)
```

```{r definition, include = FALSE}
idu <- seq_field("idu")$name
surf_ca <- seq_field("surf_cad")$name

stand <- seq_field("stand")$name
wealth <- seq_field("wealth")$name
stage <- seq_field("stage")$name
year <- seq_field("year")$name

ug <- seq_field("ug")$name
parcelle <- seq_field("parcelle")$name
sous_parcelle <- seq_field("sous_parcelle")$name
```

# What are we looking for?

Forest management (forest planning) consists in scheduling forest interventions:

-   harvesting operations that generate revenue;

-   silvicultural works that require investments.

To establish this schedule, a management parcel system (i.e. management units) is required.

A management unit corresponds to an area that is homogeneous from a forestry perspective and must therefore have a defined surface area.

The French forestry context implies a set of **common-sense principles**, while the French administration imposes some **fundamental rules**.

Among the fundamental rules, let us remember that **we work with cadastral surfaces** and not cartographic surfaces.

This package offers an integrative approach.

# 0. Sequoia definitions

## Analysis unit

An **analysis unit** (AU) corresponds to the smallest fraction of a cadastral parcel that is **homogeneous in terms of its descriptive forest attributes**, and is designated by a unique management unit (MU) identifier.

In other words, each *AU* :

-   keep its cadastral attributes in order to calculate cadastral areas: unique cadastral identifier (`r idu`) and cadastral surface (`r surf_ca`);

-   receives a forest description by filling the attribute table: stand type (`r stand`), stand wealth (`r wealth`), stand stage (`r wealth`) and year of stand establishment (`r year`) at least;

-   receives a forest management unit identifier composed by a forest parcel number (`r parcelle`) and a sub-parcel number (`r sous_parcelle`).

## Management unit

An **management unit** (MU) corresponds to an area that is homogeneous in terms of its forest description and that is managed under **a single silvicultural regime**. It is composed of several analysis units.

In other words, each *AU* of a *MU* must have :

-   the same forest description (same starting point);

-   the same forestry destiny (same point of arrival).

## Forest parcels

**Forest parcels** (FP) division corresponds to **an arbitrary subdivision** of a forest, dicided by owner or last forest manager.

***Rules to follow:***

-   If forest parcels exist, you have to work with.

-   If forest parcels exist, but are not usable, correct them by attaching them to the structural elements of the massif (roads, rivers, embankment, tracks).

-   If forest parcels doesn't exist, create them by attaching them to the structural elements. Do not use stands because forest can be evolve quickly.

# 1. How do I create the analysis unit layer?

As mentioned before, the *AU* layer must keep cadastral attribute. That's why the *AU* layer is created from the cadastral parcels layers *CP*.

## Before creation, check topology

...

## Run `seq_parca_to_ua()` and load the layer

At the time of its creation, the analysis unit layer is nothing more than the cadastral parcel layer enriched with additional attribute fields.

```{r seq_parca_to_ua, fig.height = 3.5}
ua_path <- seq_parca_to_ua(sequoia_dir)
ua <- read_sf(ua_path)

tm_tiles("OpenStreetMap")+
tm_shape(ua)+
  tm_borders(col = "firebrick", lwd = 2)
```

```{r segmentation, include = FALSE}
qgis <- "https://qgis.org/"
```

# 2. How do I work with the analysis unit layer?

Our approach consists of dividing cadastral parcels into fractions (the units of analysis), according to logical steps.

This segmentation can only be performed using GIS software. We strongly recommend the [Quntum GIS suite](%60r%20qgis%60).

As segmentation steps, we recommend :

1.  Start with roads right-of-way;
2.  Continue with forest parcels limits;
3.  Continue with important tracks;
4.  Finally, distinguish the stand.

At each step, the user is required to complete the attribute fields table.

# 3. How do I obtains the cadastral area?

When you have finish to segmentize the *AU* layer, you can get validate the *UA* layer by running `seq_ua()`.

**/!\\** *The AU* layer must be closed on your GIS software before running !

```{r seq_ua, fig.height = 3.5}
ua_path <- seq_ua(sequoia_dir)
ua <- read_sf(ua_path)

tm_tiles("OpenStreetMap")+
tm_shape(ua)+
  tm_borders(col = "firebrick", lwd = 2)
```

This function overwrite the *AU* layer: it's the same layer, but with:

-   IDUs checked against PARCA;

-   cadastral areas checked and corrected;

-   management unit fields generated; - corrected cadastral areas added;

-   management unit consistency checked and corrected.

# 4. How can I use the updated *AU* layer after ?

When you have updated the *AU* layer, you can get new products:

-   **PF (Parcelle)**: Rows of the *AU* are grouped using the `parcelle` field, and corrected surface areas (`surf_cor`) are summed. A polygon and border lines layer are created.

-   **SSPF (Sous-parcelle)**: Rows of the *AU* are grouped using the `r parcelle` and `r sous_parcelle` field, and corrected surface areas (`surf_cor`) are summed. A polygon and border lines layer are created.

```{r seq_parcels, fig.height = 3.5}
# generate new products by running
paths <- seq_parcels(sequoia_dir)

# read new product
pf_poly   <- st_read(paths[[1]], quiet = TRUE)
pf_line   <- st_read(paths[[2]], quiet = TRUE)
sspf_poly <- st_read(paths[[3]], quiet = TRUE)
sspf_line <- st_read(paths[[4]], quiet = TRUE)

# view
tmap_mode("view")

tm_shape(pf_line) +
  tm_lines(col = "blue", lwd = 3) +

tm_shape(pf_poly) +
  tm_text("N_PARFOR", col = "blue", size = 0.8) +

tm_shape(sspf_line) +
  tm_lines(col = "black", lwd = 1) +

tm_shape(sspf_poly) +
  tm_text("PARFOR", col = "black", size = 0.7)

```
