---
title: "Cadastral parcels - legal entity"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Cadastral parcels - legal entity}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup}
knitr::opts_chunk$set(
  collapse = TRUE,
  out.width = "100%",
  dpi = 300,
  fig.width = 7.2916667,
  comment = "#>"
)
```

```{r, echo = FALSE, message = FALSE}
library(tmap)
tmap_options(scale = 0.75)
```

```{r package}
library(Rsequoia2)
library(tmap)
library(openxlsx2)
library(sf)
```

As always, we need to setup a Sequoia dir (temporary in this case)

```{r setup_seqdir}
seq_dir <- file.path(tempdir(), "MY_FOREST")
dir.create(seq_dir)
```


# What is Legal Entity.

In France, legal entity is known as "Personne morale". Unlike a physical person, a legal entity has its own juridical existence and is identified by national codes such as SIREN or SIRET. In Forestry, typical entities include "groupements forestiers" or companies.

France provides open datasets that describe all cadastral parcels owned by legal entities. These files, published by the ***Direction Générale des Finances Publiques** (DGFiP), allow users to retrieve cadastral parcels for a given owner.

`Rsequoia2` give acces to this dataset and helpers to search specific owner.

## Retrieve legal entity owner

`get_legal_entity()` function download and prepare data as a Sequoia matrice. 

There is a cache system to this function to avoid downloading each time. By default `cache = NULL` which downlaod data in a dedicated cache dir (see `tools::R_user_dir()`).

You should keep this directory but if for any reason you need raw data elsewhere use `cache` arg.

Be aware that you can load data from a department code or an insee code. The first can be a bit time-consuming but you can then search all selected dep(s) if owner have cadastral parcels accros multiple commune.

```{r get_legal_entity}
# cp: cadastrals parcels
insee <- c("29158", "29165")

legal_entity_cp <- get_legal_entity(insee)

head(legal_entity_cp)
```
## Search legal entity owner

After loading the file you can use helpers `search_legal_entity()`. 

This helpers relies on a text–normalization applied to both the inputs and the corresponding columns of the matrice. This makes the search robust to accents, punctuation, spacing irregularities and case differences.

Below we search all GFA ("Groupement Foncier Agricole").

```{r search_legal_entity}
search_mat <- search_legal_entity(legal_entity_cp, prop = "gfa")

unique(search_mat$PROPRIETAIRE)
```

`search_legal_entity()` can also support multiple search pattern:

```{r search_legal_entity_multiple}
search_mat <- search_legal_entity(legal_entity_cp, prop = c("conservatoire", "espace", "naturel"))

unique(search_mat$PROPRIETAIRE)
```

Finally, `lieu_dit` can also be seached:

```{r search_legal_entity_lieu_dit}
search_mat <- search_legal_entity(legal_entity_cp, lieu_dit = "phare")

unique(search_mat[,c("PROPRIETAIRE", "LIEU_DIT")])
```

## Save to start Sequoia process

Note that *the legal entity dataset doesn't provide geometry !* It's used to generate an excel matrice ("*_matrice.xlsx") to start a Sequoia process. `seq_xlsx()` function can be used to generate it.

Notice that the `data.frame` generated with `get_legal_entity()` is already formated for Sequoia process. This mean you have the `"IDENTIFIANT"` columns. To avoid filling it in excel, we encouraged you to do it before saving.

```{r save_legal_entity}
id <- "MY_FOREST"
search_mat$IDENTIFIANT <- id

seq_write(
  x = search_mat,
  key = "matrice",
  dirname = seq_dir,
  id = id
)

seq_parca(seq_dir)
parca <- seq_read("parca", seq_dir)

tm_tiles("OpenStreetMap")+
tm_shape(parca)+
  tm_borders(col = "firebrick", lwd = 2)
```

