---
title: "Sequoia"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Sequoia}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup}
knitr::opts_chunk$set(
  collapse = TRUE,
  out.width = "100%",
  dpi = 300,
  fig.width = 7.2916667,
  comment = "#>"
)
```

```{r, echo = FALSE, message = FALSE}
library(tmap)
tmap_options(scale = 0.75)
```

```{r package}
library(Rsequoia2)
library(tmap)
library(openxlsx2)
library(sf)
```

# What is Sequoia

Sequoia is an opiniated way of dealing with forest management. It's goal is to :

- Facilitate downloading of data for forest management ;
- Normalize data (name and structure) ;
- Facilitate exploration of those data

# How it works 

## Internal configuration

`Rsequoia2` relies on an internal configuration that maps keys to data layers and their metadata.
For example, the key `"r.sol.geol"` refers to the geological raster layer named `GEOL.tif`.

All available keys can be listed with `seq_layer()`. To access metadata for a specific layer, use `seq_layer("r.sol.geol")`.

Note that full keys are not always required: `seq_layer("geol")` also works.

##`seq_*` functions

All main functions in `Rsequoia2` start with `seq_*` (e.g. seq_geol(), seq_prsf(), ...).

These functions:
- Read the project cadastral parcels to defined area of interest ;
- Download the required data ;
- Save them according to the configuration (name and extension) ;
- Return path(s) where the data are stored.

_Note: for advanced users, each `seq_*` function has an equivalent `get_*` function (e.g. `get_geol()`, `get_prsf()`, ...). These can be used independently of the Sequoia workflow._

## Reading data

`seq_read()` uses the configuration to read any layer using its key (vector or raster).

```{r read_data}

parca <- seq_read("parca")
dem <- seq_read("dem")

```

# What is a Sequoia process

Sequoia process always have those step :

- Setting a directory ;
- Creating parca matrice (excel with cadastrals parcels info);
- Downloading parca geometry;
- Downloading data based on parca;
- GIS part to create analysis units ;
- Generating final layer from analysis units

# Setting a directory

All `seq_*` function have `dirname = "."` argument, meaning they use the current working directory by default. Best practice is to create a dedicated directory and set it as the working directory for the R session.

For the example, a forest named `"ECKMUHL"` is used:

```{r eval=FALSE, warning=FALSE}
sequoia_dir <- "ECKMUHL"
dir.create(sequoia_dir)

# setting current dir to our sequoia dir
setwd(sequoia_dir)
```

# Creating parca matrice

`Rsequoia2` provides several ways to generate this fundamental file:

- A manually filled empty Excel file (see Cadastral Parcels article)
- Using legal-entity open data (see Cadastral Parcels – Legal Entity article)
- Generating the file from DGFiP PDF matrices

# Downloading parca geometry

All data downloaded by `Rsequoia2` are based on cadastral parcels (parca). The first mandatory step is therefore to download them using `seq_parca()`.

```{r download_parca, eval=FALSE}
seq_parca()
```

# Downloading data

`Rsequoia2` offer many datasets, which can be downloaded using `seq_*` functions:

- Environnemental data from MNHN ;
- Elevation data from IGN ;
- Orthophoto data from IGN ;
- Geological data from BRGM ;
- Hydrological data from BD Topo IGN ;
- Patrimony data from Atlas du Patrimoine ;
- ...

```{r, eval=FALSE}
mnhn <- seq_mnhn()
```

As explained above, all data are saved in the current directory by default. If you need a more structured folder layout, you can provide a custom `dirname`.

In the example below, raster and vector data are stored in separate directories:

```{r downloading_data, eval=FALSE}
vdir <- file.path(sequoia_dir, "VECTOR")
rdir <- file.path(sequoia_dir, "RASTER")

seq_parca(vdir)
seq_mnhn(vdir)
seq_elevation(rdir)
seq_ortho(rdir)
seq_geol(vdir)
seq_hydro(vfdir)
seq_patrimony(vdir)

```

# GIS part

...

# Finalizing layer

..

# How it can be used

Sequoia is created thinking that power user and friendly user will use it. This is reflected by the name of function. All function starting with `seq_*` are wrapper around low level function for friendly user.



